Urban Crime Dynamics: Trends in Theft and Assault Over 2014 to 2023

### 2024-09-26 paper/paper.qmd
change the appendix part

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

## Diagnostics

>>>>

# Dataset and Graph Sketches {#sec-appendix-sketches}

The dataset used in this paper, and the related sketches generated from the dataset, can be found in the folder named 'sketches' in the folder named 'other' in the GitHub repository

# Additional data details {#sec-appendix-cleaning}

The process of data cleansing is to extract the columns required for data analysis in this paper and store them in a new csv file.
